Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2016-12-20 Code/append_smoothed_results.Rmd
Added census region to BW dataset

BlackWhite <- BlackWhite3
rm(BlackWhite3, BlackSmooth, WhiteSmooth)
```

>>>>

BlackWhite <- BlackWhite3
rm(BlackWhite3, BlackSmooth, WhiteSmooth)

BlackWhite$Census_Region <- "South"
BlackWhite$Census_Region[BlackWhite$State2 %in% c("Iowa", "Kansas", "Minnesota", "Missouri", 
                                                 "Nebraska", "North Dakota", "South Dakota", 
                                                 "Illinois", "Indiana", "Michigan", "Ohio", 
                                                 "Wisconsin")] <- "Midwest"

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Connecticut", "Maine", "Massachusetts", 
                                                 "New Hampshire", "Rhode Island", "Vermont",
                                                 "New Jersey", "New York", "Pennsylvania")] <- "Northeast"

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Arizona", "Colorado", "Idaho", "Montana", 
                                                 "Nevada", "New Mexico", "Utah", "Wyoming",
                                                 "Alaska", "California", "Hawaii", "Oregon",
                                                 "Washington")] <- "West"
```

### 2016-12-20 Manuscript/Manuscript.Rmd
Added census region to BW dataset

>>>>

**Figure 5: Trends in the black-white life expectancy gap for males between 1969 and 2013 by US state**
```{r figure5, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhiteSmooth, Sex2 == "Male"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2)))
```

**Figure 6: Trends in the black-white life expectancy gap for females between 1969 and 2013 by US state**
```{r figure5, fig.align="center", fig.height=8, fig.width=8, echo=F}
ggplotly(ggplot(subset(BlackWhiteSmooth, Sex2 == "Female"), aes(y=WBgap.s, x = Year3)) + geom_line(aes(col = State2)))
```
